Evaluating computational methods for modeling off-normal operation of gas centrifuge cascades

### 2018-06-27 theory.tex
intagrating some gonuke comments

\begin{table}[htb]
\centering
\caption{Summary of the centrifuge parameters.}
\begin{tabular}{cccccccc}
\toprule
$T$[K] & $v$[m/s]    & $h$[m] & $d$[m]   & $x$   & $F$[mg/s]  & $L/F$ & $e$  \\
\midrule
320    & $320$           & $1.8$ & $0.105$ & $1e3$  & $13$      & 2     & 1.0  \\
\bottomrule
\end{tabular}

@@

The cascade is built as an ideal cascade, with no losses in the separative work,
which corresponds to $\alpha =\beta = const$ for all stages of the cascade, where
$\alpha$ and $\beta$ respectively represent the feed to product and the feed to
tail enrichment factors.  $\alpha$ and $\beta$ can be expressed as function of
the abundance ($R$) or the enrichment ($N$) of respectively the product
($R'$, $N'$) and the feed ($R$, $N$) and the feed and the tails ($R''$, $N''$) such
as:
\begin{subequations} \label{eqs:alphabeta}
    \begin{equation} \label{eq:alpha_def}
        \alpha = \frac{R'}{R} = \frac{N'}{1-N'}\frac{1-N}{N} 
\end{equation}
\\
\begin{equation}\label{eq:beta-def}
        \beta = \frac{R}{R''} = \frac{N}{1-N}\frac{1-N''}{N''} 
\end{equation}
\end{subequations}

@@

From the mass conservation, $N = \theta N' + (1-\theta)N''$, and equations
\eqref{eqs:alphabeta} it is possible to express $\beta$ as a function of the
feed abundance, $R$, the cut $\theta$ and $\alpha$:

@@

From equation \eqref{eq:alpha} and \eqref{eq:beta} it is possible to determine
the cut, $\theta$, or the ratio of product flow to feed flow required to build an ideal
cascade:
$\beta$ values and the feed assay, $N_{i}$:
\begin{eqnarray}
    \theta_{i} = \dfrac{N_{i} - \dfrac{1}{1 + \beta/R_{i}}}{ \dfrac{\alpha R_{i}}{1 + \alpha R_{i}} -
           \dfrac{1}{1 + \beta/R_{i}}}
\end{eqnarray}

As $\alpha_{i}$ and $\beta_{i}$ remain constant, only the value of the cut,
$\theta_{i}$, changes across the different stages of a cascade.  This algorithm
assumes that the corresponding separative power $\delta U$ (not re-computed) can
be achieved with the chosen centrifuge design, tuning other operational
parameter such as the rotation speed, the counter-current flow ratio...  Once
$\theta_{i}$ is determined, it is possible to compute the product and the tail
assay.

@@

\subsection{Miss-use models}

@@

\begin{table}[htb]
\centering
  \caption{Summary of miss-use model properties.}
\begin{tabular}{l|ccc}
\toprule

Model                &    A                 & B                  & C  \\
\midrule
Constant parameters  & $\alpha_i, \theta_i$ & $\alpha_i=\beta_i$ & $\gamma_i=\alpha_i*\beta_i, \theta_i$       \\
Optimised parameters & $\beta_i$            & $\theta_i$         & $\alpha_i, \beta_i$                     \\
Assays determination & blended              & ideal              & blended                  \\
Flow                 & unchanged            & scaled             & unchanged       \\

@@

In order to compute the proper product and tails assay at each stage, the tails
and the product from respectively the next and the previous stage must be
blended in order to determine the correct stage feed assay. As this is a obvious
cycling problem, an iterative solution has been chosen: all feed assays are
iteratively updated, blending the proper product and tails, then using the
updated feed assay, the new product and tail assays are recomputed. This process
is repeated until the sum of the square difference in assays is smaller than the
precision (1e-8).  As the cut remain fixed at each stage the different flow do
not need to be recomputed.

@@

The second method the cut value at each stage $\theta_i$, is retuned in order to
maintain the $\alpha_i$ and $\beta_i$ at their original values. As the cascade
remains ideal, the product and tail assay at each stages (and for the overall
cascade) is easily determined using equations \eqref{eqs:alphabeta}.

As the cuts values change, the flow rate between the different stage has to be
recomputed. Because the cascade is not reorganised (the number of cascade per
stage remain the same as the original design). The new flow rate are computed as
the flow rates of the reconfigured cascade scaled down to match the allowed
flows of the original one: the flow rates at each stage of a miss-used cascade
have to be inferior or equal to the initial cascade design.

\subsubsection{Model C}
The last model assumes that the tail to product enrichment factor remains
constant regardless to the feed assays. To compute the response of the cascade
one need to determine $\alpha$ and $\beta$ such as their product and
$\theta$ remain fixed. 
From equations \eqref{eqs:alphabeta} and the assay conservation equation $N =
\theta N' + (1-\theta)N''$ it is possible to express the product $N'$ as a function of
the feed assay $N$, $\gamma$ and the cut $\theta$ as one solution of the second
order equation \eqref{eq:gamma_p}:

@@

The only solution allowing product assay to range between 0 and 1 is the
following :
\begin{equation}\label{eq:model_b_sol}
    \frac{\gamma(N + \theta) - N 
            - \sqrt{\gamma^2(N^2 
                            - 2N\theta 
                            + \theta^2) 
                    - \gamma(2N^2 - 2\theta^2 
                            + 2N + 2\theta) 
                    + N^2 + 2N\theta + \theta^2 - 2N - 2\theta + 1} 
            - \theta + 1}
        {2\theta(\gamma - 1)}
\end{equation}
Once the product assay is known, one can trivially determine the tail assay,
$\alpha$ and $\beta$ using equations \eqref{eqs:alphabeta} and mass
conservation.

>>>>

\begin{table}[htb]
\centering
\caption{Summary of the centrifuge parameters.}
\begin{tabular}{cccccccc}
\toprule
$T$[K] & $v$[m/s]    & $h$[m] & $d$[m]   & $x$   & $F$[mg/s]  & $L/F$ & $e$  \\
\midrule
320    & $320$       & $1.8$  & $0.105$  & $1^{3}$ & $13$       & 2     & 1.0  \\
\bottomrule
\end{tabular}

@@

The cascade is built as an ideal cascade, with no losses in the separative work,
which corresponds to $\alpha =\beta = const$ for all stages of the cascade, where
$\alpha$ and $\beta$ respectively represent the feed to product and the feed to
tails enrichment factors.  $\alpha$ and $\beta$ can be expressed as function of
the abundance ($R$) or the enrichment ($N$) of respectively the product
($R'$, $N'$) and the feed ($R$, $N$) and the feed and the tails ($R''$, $N''$) such
as:
\begin{subequations} \label{eq:alphabeta}
    \begin{equation} \label{eq:alpha_def}
        \alpha = \frac{R'}{R} = \frac{N'}{1-N'}\frac{1-N}{N} 
\end{equation}
\\
\begin{equation}\label{eq:beta-def}
        \beta = \frac{R}{R''} = \frac{N}{1-N}\frac{1-N''}{N''} 
\end{equation}
\end{subequations}

@@

From the mass conservation, $N = \theta N' + (1-\theta)N''$, and equations
\eqref{eq:alphabeta} it is possible to express $\beta$ as a function of the
feed abundance, $R$, the cut $\theta$ and $\alpha$:

@@

From equation \eqref{eq:alpha} and \eqref{eq:beta} it is possible to determine
the cut, $\theta$ required to build an ideal cascade:
\begin{eqnarray}
    \theta_{i} = \dfrac{N_{i} - \dfrac{1}{1 + \beta/R_{i}}}{ \dfrac{\alpha R_{i}}{1 + \alpha R_{i}} -
           \dfrac{1}{1 + \beta/R_{i}}}
           \label{eq:theta}
\end{eqnarray}

As $\alpha_{i}$ and $\beta_{i}$ remain constant, only the value of the cut,
$\theta_{i}$, changes across the different stages of a cascade.  This algorithm
assumes that the corresponding separative power $\delta U$ (not re-computed) can
be achieved with the chosen centrifuge design, tuning other operational
parameter such as the rotation speed, the counter-current flow ratio, etc.  Once
$\theta_{i}$ is determined, it is possible to compute the product and the tail
assay.

@@

\subsection{Misuse models}

@@

\begin{table}[htb]
\centering
  \caption{Summary of misuse model properties.}
\begin{tabular}{l|ccc}
\toprule

Model                &    A                 & B                  & C  \\
\midrule
Constant parameters  & $\alpha_i, \theta_i$ & $\alpha_i=\beta_i$ & $\gamma_i=\alpha_i .\beta_i, \theta_i$       \\
Varying parameters   & $\beta_i$            & $\theta_i$         & $\alpha_i, \beta_i$                     \\
Assays determination & blended              & ideal              & blended                  \\
Flow                 & unchanged            & reduced            & unchanged       \\

@@

In order to compute the proper product and tails assay at each stage, the tails
and the product from the next and the previous stage respectively must be
blended in order to determine the correct stage feed assay. All feed assays are
iteratively updated, blending the proper product and tails, then using the
updated feed assay, the new product and tails assays are recomputed. This
process is repeated until the sum of the square difference in assays is smaller
than $1^{-8}$.  As the cut remain fixed at each stage the flows do not need to
be recomputed.

@@

Using the second method, the cut value at each stage $\theta_i$, is retuned in
order to maintain the $\alpha_i$ and $\beta_i$ at their original values
(equation \eqref{eq:theta}). As the cascade remains ideal, the product and tails
assay at each stages are easily determined using equations \eqref{eq:alphabeta}.

As the cut values change, the relative flow rates between the different stage
are recomputed using equation \eqref{eq:flow}. The new flows are also
constrained by the fixed design of the cascade, number of centrifuges limiting
the flow at each level.

\subsubsection{Model C}
The last model assumes that the tails to product enrichment factor remains
constant regardless to the feed assays. To compute the response of the cascade
one need to determine $\alpha$ and $\beta$ such as their product and
$\theta$ remain fixed. 
From equations \eqref{eq:alphabeta} and the assay conservation equation $N =
\theta N' + (1-\theta)N''$ it is possible to express the product $N'$ as a function of
the feed assay $N$, $\gamma$ and the cut $\theta$ as one solution of the second
order equation \eqref{eq:gamma_p}:

@@

The only solution allowing product assay to range between 0 and 1 is the
following :
\begin{equation}\label{eq:model_b_sol}
    \frac{\gamma(N + \theta) - N 
            - \sqrt{\gamma^2(N^2 
                            - 2N\theta 
                            + \theta^2) 
                    - \gamma(2N^2 - 2\theta^2 
                            + 2N + 2\theta) 
                    + N^2 + 2N\theta + \theta^2 - 2N - 2\theta + 1} 
            - \theta + 1}
        {2\theta(\gamma - 1)}
\end{equation}
Once the product assay is known, one can trivially determine the tails assay,
$\alpha$ and $\beta$ using equations \eqref{eq:alphabeta} and mass
conservation.
